---
title: "STATS506 Homework3"
author: "Haichao Ji"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r}
rm(list = ls())
setwd(getwd())
```


# (1)

Global level git configuration files locate in $C:\backslash Users\backslash username\backslash .gitconfig$ and lobal level git configuration files locate in $<git-repo>\backslash .git\backslash config$ for Windows.\\

credential.helper=osxkeychain

filter.lfs.clean=git-lfs clean -- %f

filter.lfs.smudge=git-lfs smudge -- %f

filter.lfs.process=git-lfs filter-process

filter.lfs.required=true

user.name=Symmes

user.email=haichao1121$@$gmail.com

# (2)

```{r}
readLines = function(n1,n2){
nms = read.delim("Data/2020_Business_Academic_QCQ.txt",header = FALSE, sep = ',', nrows = 1)
df = read.delim("Data/2020_Business_Academic_QCQ.txt",header = FALSE, sep = ',', nrows = n2 - n1, skip = n1, fileEncoding="latin1")
names(df) <- nms
df[df==""] <- NA
res = na.omit(df[,c(4,7,28,29,45)])
names(res) <- c("state","county_code","employee_size","sales_volume","census_tract")
res
}
```

# (3)

```{r}
df1 = data.frame(row.names = c("state","county_code","employee_size","sales_volume","census_tract"))
for(i in 1:15){
  df = readLines(20000*(i-1)+1,20000*i+1)
  df1 = rbind(df1,df)
}
```

# (4)

```{r}
library(RPostgreSQL)
drv <- dbDriver("PostgreSQL")
con <- dbConnect(drv, user='root', password='jhcbywzfb7', dbname='Hw3db')

```

